---
title: Help
output: html_fragment
params:
  help_welcome: NULL
  contact_title: NULL
  contact_info: NULL
  thanks: NULL
  important_resources: NULL
  resource_sentence: NULL
---

```{r setup, include=FALSE}
library(htmltools)
library(glue)

knitr::opts_chunk$set(
  echo=FALSE, 
  results = 'asis'
  )

person <- tags$a('Nathan M. Stall', href = "mailto:nathan.stall@mail.utoronto.ca")
```

```{r welcome-help}
p(params$help_welcome)
```

<hr />

```{r contact}
h4(params$contact_title)

p(HTML(glue(params$contact_info)))

p(params$thanks)
```

<hr />

```{r resources}
h4(params$important_resources)

p(params$resource_sentence)
```

<ul>
  <li>Barrett K, Khan Y, Mac S, Ximenes R, Naimark D, Tuite A, et al. COVID-19: Predicting Healthcare Resource Needs in Ontario 2020 [updated March 18, 2020. Available from: <a href="https://drive.google.com/drive/folders/1T5I2VKuvVFD0FmFGItcH_ZX1XioH4vYU">https://drive.google.com/drive/folders/1T5I2VKuvVFD0FmFGItcH_ZX1XioH4vYU</a>.
</li>
  <li>CDC COVID-19 Response Team. Severe Outcomes Among Patients with Coronavirus Disease 2019 (COVID-19) — United States, February 12–March 16, 2020. MMWR Morb Mortal Wkly Rep. 2020.</li>
  <li>Dong J, Perry O. Queueing Models for Patient-Flow Dynamics in Inpatient Wards. Operations Research. 2020;68(1):250-275.</li>
  <li>Grasselli G, Pesenti A, Cecconi M. Critical Care Utilization for the COVID-19 Outbreak in Lombardy, Italy: Early Experience and Forecast During an Emergency Response. JAMA. 2020.</li>
  <li>Society of Critical Care Medicine Ventilator Taskforce. U.S. ICU Resource Availability for COVID-19. <a href="https://sccm.org/getattachment/Blog/March-2020/United-States-Resource-Availability-for-COVID-19/United-States-Resource-Availability-for-COVID-19.pdf?lang=en-US">https://sccm.org/getattachment/Blog/March-2020/United-States-Resource-Availability-for-COVID-19/United-States-Resource-Availability-for-COVID-19.pdf?lang=en-US</a>. Published 2020. Updated March 19, 2020. Accessed March 19, 2020.</li>
  <li>Wang D, Hu B, Hu C, et al. Clinical Characteristics of 138 Hospitalized Patients With 2019 Novel Coronavirus-Infected Pneumonia in Wuhan, China. JAMA. 2020.</li>
  <li>World Health Organization. Coronavirus disease 2019 (COVID-19) Situation Report – 58. <a href="https://www.who.int/docs/default-source/coronaviruse/situation-reports/20200318-sitrep-58-covid-19.pdf?sfvrsn=20876712_2">https://www.who.int/docs/default-source/coronaviruse/situation-reports/20200318-sitrep-58-covid-19.pdf?sfvrsn=20876712_2</a>. Published March 18, 2020. Accessed March 19, 2020.</li>
  <li>Yang X, Yu Y, Xu J, Shu H, Xia J, Liu H, et al. Clinical course and outcomes of critically ill patients with SARS-CoV-2 pneumonia in Wuhan, China: a single-centered, retrospective, observational study. Lancet Respir Med. 2020.</li>
  <li>Zhou F, Yu T, Du R, et al. Clinical course and risk factors for mortality of adult inpatients with COVID-19 in Wuhan, China: a retrospective cohort study. Lancet. 2020.</li>
</ul>
<br />
