---
title: "COVID-19 Acute and Intensive Care Resource Tool"
subtitle: "Resource Utilization Report"
date: "__Report Generated:__ `r paste0(Sys.time(), ' ', Sys.timezone())`"
output: 
  pdf_document:
    latex_engine: xelatex
geometry: margin=1in
fontsize: 12pt
header-includes:
  - \usepackage{tcolorbox}
  - \usepackage{titling}
  - \usepackage{titlesec}
  - \usepackage{fontspec}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \pretitle{\begin{flushleft}\LARGE \vskip -3em\textsc}
  - \posttitle{\end{flushleft}}
  - \predate{\begin{flushleft}}
  - \postdate{\end{flushleft}}
  - \setmainfont{Calibri}
params:
  widgets: NULL
  table: NULL
  outputs: NULL
---

\pagenumbering{gobble}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  error = TRUE, 
  message = FALSE, 
  warning = FALSE,
  out.width = "80%"
  )

library(tidyverse)
library(scales)
library(glue)
library(knitr)
library(kableExtra)
```

\begin{tcolorbox}
\textbf{Authors:}
\begin{itemize}
  \item{Vasily Giannakeas, MPH \textsuperscript{1,2}}
  \item{Deepit Bhatia, MPH}
  \item{Matthew T. Warkentin, MSc \textsuperscript{2,3}}
  \item{Isaac I. Bogoch, MD \textsuperscript{4,5}}
  \item{Nathan M. Stall, MD \textsuperscript{1,4,6,7}}
\end{itemize}
\medskip

\textbf{Description:} CAIC-RT is an online tool capable of estimating the maximum daily number of incident COVID-19 cases that a healthcare system could manage based on age-based case distribution and severity, and the number of available acute and critical care resources.

\medskip
{\tiny
\begin{enumerate}
  \item{Women's College Research Institute, Women's College Hospital, Toronto, Ontario, Canada}
  \item{Dalla Lana School of Public Health, University of Toronto, Toronto, Ontario, Canada}
  \item{Lunenfeld-Tanenbaum Research Institute, Sinai Health System, Toronto, Ontario, Canada}
  \item{Department of Medicine, University of Toronto, Toronto, Ontario, Canada}
  \item{Divisions of General Internal Medicine and Infectious Diseases, University Health Network, Toronto, Canada}
  \item{Institute of Health Policy, Management and Evaluation, University of Toronto, Toronto, Ontario, Canada}
  \item{Divisions of General Internal Medicine and Geriatrics, Sinai Health System, Toronto, Ontario, Canada}
\end{enumerate}
}
\end{tcolorbox}

```{r widget-inputs, include=FALSE}
n_acute <- params$widgets$n_acute
n_crit <- params$widgets$n_crit
n_vent <- params$widgets$n_vent
lou_acute <- params$widgets$lou_acute
lou_crit<- params$widgets$lou_crit
lou_vent <- params$widgets$lou_vent
per_vent <- params$widgets$per_vent
```

```{r}
tribble(
  ~item, ~value,
  "Mean days in acute care", lou_acute,
  "Mean days in critical care", lou_crit,
  "Mean days on a mechanical ventilator", lou_vent,
  "Number of acute care beds", n_acute,
  "Number of critical care beds", n_crit,
  "Number of mechanical ventilators", n_vent,
  "Percent patients requiring mechanical ventilation", per_vent
) %>% 
  kable(booktabs = TRUE, format.args = list(big.mark = ','),
        caption = "Expected resource utilization and resource availability for COVID-19 patients.",
        col.names = c('Input Parameter', 'Value')) %>% 
  kable_styling(full_width = FALSE, position = 'center', latex_options = 'H')
```


```{r}
kable(params$table, booktabs = TRUE, 
      col.names = c('Age groups',
                    'Case Distribution (%)',
                    'Acute Care Admission (%)',
                    'Critical Care Admission (%)'), 
      caption = "Age-stratified case distribution and severity.") %>% 
  kable_styling(full_width = FALSE, 
                position = 'center', latex_options = 'H')
```

```{r results='asis'}
glue('Based on {params$outputs$acute$n_acute} available mechanical ventilators with an average duration of use of {params$outputs$acute$lou_acute} days, at maximum capacity the expected turnover rate is {params$outputs$acute$acuteBedRate} ventilators per day. Based on the age-stratified case distribution, the proportion of COVID-19 cases requiring mechanical ventilation is {params$outputs$acute$rateAcute} percent. Given this, your healthcare environment has the capacity to manage a maximum of {params$outputs$acute$maxAcute} incident cases of COVID-19 per day.')
```

```{r results='asis'}
glue('Based on {params$outputs$crit$n_crit} available mechanical ventilators with an average duration of use of {params$outputs$crit$lou_crit} days, at maximum capacity the expected turnover rate is {params$outputs$crit$critBedRate} ventilators per day. Based on the age-stratified case distribution, the proportion of COVID-19 cases requiring mechanical ventilation is {params$outputs$crit$rateCrit} percent. Given this, your healthcare environment has the capacity to manage a maximum of {params$outputs$crit$maxCrit} incident cases of COVID-19 per day.')
```

```{r results='asis'}
glue('Based on {params$outputs$mvent$n_vent} available mechanical ventilators with an average duration of use of {params$outputs$mvent$lou_vent} days, at maximum capacity the expected turnover rate is {params$outputs$mvent$ventBedRate} ventilators per day. Based on the age-stratified case distribution, the proportion of COVID-19 cases requiring mechanical ventilation is {params$outputs$mvent$rateVent} percent. Given this, your healthcare environment has the capacity to manage a maximum of {params$outputs$mvent$maxVent} incident cases of COVID-19 per day.')
```

